### 2018-02-20 icde/cameraready/Response.tex

The {\em PeakMul} pattern is originally defined in [18]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years. In our work, we unify the five patterns, and we only use the highest peak that has been formally defined in Section II-A (para 1, left column, page 3).
Also note that: (1) [18] allows multiple peaks to exist for an article while we only consider the highest peak, and (2) [18] uses the original numbers of citations to compute peaks, and we use the scaled numbers of citations \wrt the total number of citations of all articles at each year.

[18]  T. Chakraborty, S. Kumar, P. Goyal, N. Ganguly, and A. Mukherjee, ¡°On the categorization of scientific citation profiles in computer science,¡± Commun. ACM, vol. 58, no. 9, 2015.

\textbf{[R1D4]} \emph{For large scholar graph, such as MAG, it is better to use the distributed graph processing framework to improve the scalability of the method}

Yes, we agree that distributed processing is an important way for large scholarly graphs.  But this topic is beyond the reach of this study, and we plan to do this in our future work (Conclusions, page 12). Thanks for the suggestion!

@@

We do believe that there are technical contributions: (1) An ensemble based ranking model (a great effort needs to be paid to develop such a ranking model);  (2) An incremental algorithm designed for dynamic scholarly article ranking in the general setting, which is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics. These have never been exploited in previous studies. That is, we are not simply using known techniques for an application.

More specifically, the only existing dynamic scholarly article ranking solution [21] is based on an impractical assumption that there are no citations between articles of the same years. In this work, we study dynamic scholarly article ranking in the general setting by eliminating the strong and impractical assumption. Our incremental algorithm is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics (\eg for the maintenance of the topological order), both of which have never been exploited before.

We also believe that our ensemble based ranking model and the citation statistics revealed in our study have their own interests to the researchers in the field of scientometrics or  bibliometrics.

We have further clarified these both in the contributions and in the related work.

### 2018-02-20 icde/cameraready/sec-exp.tex

\stitle{Exp-5: Impacts of parameters}.
%\subsubsection{Exp-4: Impacts of parameters}.
In the last set of tests, we evaluated the impacts of time decaying factor $\sigma$, importance weighting factor $\lambda$, aggregating parameters $\alpha$ and $\beta$, and the TWPageRank. We fixed these parameters as well as $Y_s$ to their default values, used the TWPageRank proposed in this work by default, and tested the \PairAcc with the entire \recom and \fcita (\ie $T_p=+\infty$, $dif=1$).

@@

The TWPageRank has small impacts on efficiency, and the running time of the two algorithms only varies (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.

\eat{
With the increment of $\lambda$, \ensemblerank has more promotion than DRank and the \PairAcc of DRank is better than \ensemblerank with small $\lambda$, possibly due to the addition of popularity will correct the mistaken pairs better on DRank, although \ensemblerank rank more pairs correctly.
In addition, the change of \PairAcc with \recom is higher than the one with \fcita, possibly due to the article pairs in \fcita are of the same years.
Moreover, the \PairAcc of \ensemblerank is better than its counterparts from $\lambda=0.5$ to $\lambda=1$, except on \aminer with \fcita. Recall that in Fig.~\ref{exp-aminer-lambda} using popularity alone gives the best results on \aminer, indicating that the prestige computed by TWPageRank is less accurate on \aminer than on the other two datasets.
%
Indeed, with \recom and \fcita, the \PairAcc of \ensemblerank is (2.20\%, 6.63\%, 5.68\%) and (0.25\%, 0.05\%, 0.05\%) higher than DRank on (\aan, \aminer, \magdata), respectively, when using prestige alone, and is (1.73\%, 2.97\%, 2.92\%) and (0.22\%, -0.08\%, 0.17\%) higher when combining prestige and popularity, respectively, on average.
%
Finally, the TWPageRank has little impacts on efficiency, and the running time of \ensemblerank and its counterparts only changes (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.
}

\stitle{Summary}.
From these tests we find the followings.

>>>>

\stitle{Exp-5: Impacts of parameters}.
%\subsubsection{Exp-4: Impacts of parameters}.
In the last set of tests, we evaluated the impacts of time decaying factor $\sigma$, importance weighting factor $\lambda$, aggregating parameters $\alpha$ and $\beta$, and the TWPageRank. We fixed these parameters as well as $Y_s$ to their default values, used the TWPageRank proposed in this work by default, and tested the \PairAcc with the entire \recom and \fcita ($T_p=+\infty$, $dif=1$).

@@

The TWPageRank has a minor impact on efficiency, and the running time of the two algorithms only varies (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.

\eat{
With the increment of $\lambda$, \ensemblerank has more promotion than DRank and the \PairAcc of DRank is better than \ensemblerank with small $\lambda$, possibly due to the addition of popularity will correct the mistaken pairs better on DRank, although \ensemblerank rank more pairs correctly.
In addition, the change of \PairAcc with \recom is higher than the one with \fcita, possibly due to the article pairs in \fcita are of the same years.
Moreover, the \PairAcc of \ensemblerank is better than its counterparts from $\lambda=0.5$ to $\lambda=1$, except on \aminer with \fcita. Recall that in Fig.~\ref{exp-aminer-lambda} using popularity alone gives the best results on \aminer, indicating that the prestige computed by TWPageRank is less accurate on \aminer than on the other two datasets.
%
Indeed, with \recom and \fcita, the \PairAcc of \ensemblerank is (2.20\%, 6.63\%, 5.68\%) and (0.25\%, 0.05\%, 0.05\%) higher than DRank on (\aan, \aminer, \magdata), respectively, when using prestige alone, and is (1.73\%, 2.97\%, 2.92\%) and (0.22\%, -0.08\%, 0.17\%) higher when combining prestige and popularity, respectively, on average.
%
Finally, the TWPageRank has few impacts on efficiency, and the running time of \ensemblerank and its counterparts only changes (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.
}

\stitle{Summary}.
From these tests, we find the followings.

### 2018-02-20 icde/cameraready/sec-incAlg.tex

Our incremental algorithm \incensemble incrementally computes the popularity and prestige of associate entities.
We consider that an update $\Delta$ = $\Delta V\cup\Delta E$ is added to a (citation or venue) graph $G(V, E)$,
and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citations obey a natural temporal order, \ie an article only cites those published earlier, %, and it is rare for the mutual citations between two articles published in the same time.
\markedb{and set $|\Delta |= |\Delta V|+|\Delta E|$.}

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
%
\noindent where $Pop^+_c(v)$ (resp. $Pop_c(v)$) is the popularity of node $v$ on $G^{c,+}$ (resp. $G^c$), and
$T^+_0$ (resp. $T_0$) is the current time on $G^{c,+}$ (resp. $G^c$).
%
\eat{By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time.}
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.
\markedb{By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta G^c|)$ time.}

@@

%Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta V|+|\Delta E|)$ time,
\markedb{Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta G|)$ time,}
(b) updating the TWPageRank scores of nodes in $V_B$ and $V_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, where $t^+$ is  the maximum number of iterations among all \sccs in $G_B$ and $G_C$, and, finally, (c) updating the scores of nodes in $V_A$ costs $O(|V_A|)$ time. From these, the following holds.

@@

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively, shown in Table~II.
%
%(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only,
\markedb{(a) It saves $O(|G^c|)$ and $O(|G^v|)$ time when maintaining \sccs and the topological order based on the update data only,}
%where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
where ($|V|$, $|E|$) are more than (92\%, 89\%) of ($|V^{+}|$, $|E^{+}|$) on all tested citation and venue graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of total;
Finally, (d) it is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

>>>>

Our incremental algorithm \incensemble incrementally computes the popularity and prestige of associate entities.
We consider that an update $\Delta$ = $\Delta V\cup\Delta E$ is added to a (citation or venue) graph $G(V, E)$,
and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citation relationships obey a natural temporal order, \ie an article only cites those published earlier, and it is rare for the mutual citations between two articles published in the same time.
%\markedb{and set $|\Delta |= |\Delta V|+|\Delta E|$.}

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
%
\noindent where $Pop^+_c(v)$ (resp. $Pop_c(v)$) is the popularity of node $v$ on $G^{c,+}$ (resp. $G^c$), and
$T^+_0$ (resp. $T_0$) is the current time on $G^{c,+}$ (resp. $G^c$).
%
By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time.
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.
%\markedb{By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta G^c|)$ time.}

@@

Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta V|+|\Delta E|)$ time,
%\markedb{Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta G|)$ time,}
(b) updating the TWPageRank scores of nodes in $V_B$ and $V_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, where $t^+$ is  the maximum number of iterations among all \sccs in $G_B$ and $G_C$, and, finally, (c) updating the scores of nodes in $V_A$ costs $O(|V_A|)$ time. From these, the following holds.

@@

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively, shown in Table~II.
%
(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only,
%\markedb{(a) It saves $O(|G^c|)$ and $O(|G^v|)$ time when maintaining \sccs and the topological order based on the update data only,}
%where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
where ($|V|$, $|E|$) are more than (92\%, 89\%) of ($|V^{+}|$, $|E^{+}|$) on all tested citation and venue graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of total;
Finally, (d) it is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

### 2018-02-20 icde/cameraready/sec-intro.tex

\sstab(1) We first  propose a \underline{S}cholarly \underline{A}rticle \underline{Rank}ing model, referred to as \ensemblerank, by assembling the importance of three classes of entities (articles, venues and authors) for scholarly article ranking (Section \ref{sec-model}).
%
The importance is a combination of {\em prestige} and {\em popularity} to capture the evolving nature of entities.
%
To compute the prestige of articles and venues, we propose a novel {\em Time-Weighted PageRank} with a time decaying factor based on the citation statistics (instead of simple exponential decay), and the prestige of authors is the average prestige of all their published articles.
%
The popularity of an article is the sum of all its citation freshness (how close to the current year), while the one of venues and authors is the average popularity of their associated articles.
%
%Observe that (a), intuitively, prestige favors articles with many citations soon after their publication, and popularity favors those with recent citations, and (b) both prestige and popularity capture the evolving nature of entities.
%
To our knowledge, our Time-Weighted PageRank is among the first to incorporate diverse citation patterns of individual articles and to exploit citation statistics for scholarly article ranking.
%and the long-term bias caused by the dynamic nature of data

\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank %\markedb{and show its efficiency advantage in terms of an analysis of the citation characteristics and a specific structural property of scholarly graphs.}
in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.

\sstab(3)
We further develop an incremental algorithm for dynamic scholarly article ranking (Section~\ref{sec-incAlg}), which partitions graphs into  {\em affected and unaffected areas}, and employs different updating strategies for nodes in affected and unaffected areas.

>>>>

\sstab(1) We first  propose a \underline{S}cholarly \underline{A}rticle \underline{Rank}ing model, referred to as \ensemblerank, by assembling the importance of three classes of entities (articles, venues and authors) for scholarly article ranking (Section \ref{sec-model}).
%
The importance is a combination of {\em prestige} and {\em popularity} to capture the evolving nature of entities.
%
To compute the prestige of articles and venues, we propose a novel {\em Time-Weighted PageRank} with a time decaying factor based on the citation statistics (instead of simple exponential decay), and the prestige of authors is the average prestige of all their published articles.
%
The popularity of an article is the sum of all its citation freshness (closeness to the current year), while the one of venues and authors is the average popularity of their associated articles.
%
%Observe that (a), intuitively, prestige favors articles with many citations soon after their publication, and popularity favors those with recent citations, and (b) both prestige and popularity capture the evolving nature of entities.
%
To our knowledge, our Time-Weighted PageRank is among the first to incorporate diverse citation patterns of individual articles and to exploit citation statistics for scholarly article ranking.
%and the long-term bias caused by the dynamic nature of data

\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank %\markedb{and show its efficiency advantage in terms of an analysis of the citation characteristics and a specific structural property of scholarly graphs.}
%in which we propose a block-wise method for Time-Weighted PageRank
in terms of an analysis of the citation characteristics of scholarly articles.

\sstab(3)
We further develop an incremental algorithm for the block-wise algorithm
to deal with dynamic scholarly article ranking (Section~\ref{sec-incAlg}), which partitions graphs into  {\em affected and unaffected areas}, and employs different updating strategies for nodes in affected and unaffected areas.
